---
title: "Introduction-tracy"
output: html_document
---

To create a chunk box click on insert, R 

# Ex.1 

Install some useful packages(tydiverse, ggplot2), once the package is install in your R, it will install for every future project, you will create. However, you will need to use library() function each time you will need to use it.
```{r}
#install the packages

```

Usually, the setup file will be used for this. This will be explained later.

# Ex.2

Get familiar with R operations, compute this formula 
\[
\text{RMSE} = \sqrt{\frac{1}{m} \left(\hat{\boldsymbol{\beta}}\mathbf{x} - y \right)^2}
\]

if you print(RMSE) you should get
[1] 0.5773503

Note that you can write math function like this.

```{r}
b<-1
x<- 3
y<-2
m<-3


```


# Ex.3

Create a vector x that contain integers between 21 and 29 included.

To check your answer:

The output of print(x[1:3]) is

[1] 21 22 23

```{r}

```


# Ex.4

You will learn how to do matrices and operations on them.

Copy x row-wise into a 3 x 3 matrix y. Then, create the 3 x 3 matrix z as the matrix square of y. 

Hint: think about the difference between ^ and %*%.

To check your answer:

The output of print(z[1:2, 1:2]) is

     [,1] [,2]
[1,] 1590 1656
[2,] 1806 1881

```{r}

```



# Ex.5

Change the row names of z and the columns of y to c("a", "b", "c").

To check your answer:

The output of print(y[1:2, 1:2]) is

      a  b
[1,] 21 22
[2,] 24 25
```{r}

```

# Ex.6

Create a vector v1 containing the integers from -6 to 6.

To check your answer:

The output of print(v1[1:3]) is

[1] -6 -5 -4

```{r}

```

Then, copy v1 into a vector v2 and add the names 'odd' or 'even' based on whether the corresponding element is odd or even.

To check your answer:

The output of print(v2[1:3]) is

even  odd even
  -6   -5   -4

Hint: you can use a for loop and a if 
```{r}

```


